### 2021-03-14 paper.Rmd
added cubes example

The focus of this review will be on linear projections, in particular, as provided by the grand tour [@Asimov1985-xr; @Buja2005-cx]. The reason being that it is not feasible to adequately the very large area of visualising high-dimensions, and there have been numerous developments in tours recently.  An overview of the technique, and new modifications is provided, along with how these techniques can be used in a variety of applications, and to help understand nonlinear dimension reduction results.

>>>>

The term "high-dimensional" here means Euclidean space. Figure \ref{fig:cubes} shows a way to imagine this. It shows a sequence of cube wireframes, ranging from 1D through to 6D, where beyond 2D is a linear projection of the cube. As dimension increase, a new orthogonal axis is added. For cubes, this is achieved by doubling the cube: a 2D is two 1D cubes, a 3D is two 2D cubes, and so forth.

\begin{figure*}[!h]
\centerline{\includegraphics[width=0.95\textwidth]{figures/cubes.png}}
\caption{Illustrating what is meant by "high-dimensional" in this paper, and a "linear projection". From a sequence of increasing dimension cubes, from 1D to 6D, as wireframes, it can be seen that the as dimension increase by 1, the cube doubles}
\label{fig:cubes}
\end{figure*}

The focus of this review will be on visualising high-dimensional data using linear projections, in particular, as provided by the grand tour [@Asimov1985-xr; @Buja2005-cx]. The reason being that it is not feasible to adequately the very large area of visualising high-dimensions, and there have been numerous developments in tours recently.  An overview of the technique, and new modifications is provided, along with how these techniques can be used in a variety of applications, and to help understand nonlinear dimension reduction results.
